Performance comparison of Dask and Apache Spark on HPC systems \HL{for Neuroimaging}

### 2022-09-10 latex/paper.tex
[TMP] [WIP] fixed more comments.

\HL{
	% TODO add caveats to avoid when using the engines.

}

@@

\HL{
	% TODO discuss UCX and other high performance networks.???

}

>>>>

\HL{
	% TODO reread this paragraph.
	While the engines showed similar performance, they both come with their ow caveat that
	can drastically affect their performance.
	For Dask, the user should be aware of the Python GIL limitations.
	For Python code multiples worker processes should be used and for code releasing the
	GIL a balance between processes and thread is recommended.
	For Spark, we experienced severe performance issues due to workers running out of memory.
	Users should pay careful attetion to their Spark worker configurations to prevent similar issues.
}

@@

\HL{
	% TODO reread paragraph
	While both Dask and Spark support various high-performance network strategies
	such as UCX, we focused on the stand point on neuroscientist that would 
	commonly use the frameworks mostly out-of-the-box.
	With higher network throughput, the overall performance of the engines could differ.
	Further work would be required to compare Dask and Spark using different high-performance
	network protocols.
}
